Reduced Nucleotide Diversity on a Plant Y Chromosome Following Recent Recombination Suppression

### 2016-10-31 manuscript.tex
fixed sw latex fail in methods

To parameterize the forward simulations, we estimated the distribution of fitness effects of deleterious mutations (DFE) using our polymorphism data on the X-chromosome with the program DFE-alpha (Keightley and Eyre-Walker ref). This program fits a gamma distribution of selection coefficients to the observed frequency distribution of nonsynonymous and synonymous polymorphism from the population genetic analyses above. We used this estimated gamma distribution in our forward simulations. To examine the expected reduction in diversity, we varied the number of sites under selection, and obtained an approximate likelihood surface for our observed data based on the proportion of simulations that matched the observed estimate of pi_synonymous . To make the simulation output comparable to our data, we initialized the simulations with our empirically estimated autosomal $\theta$, adjusted for the expected neutral reduction in effective population size on the Y chromosome under a sex ratio of Nf/(Nf+Nm)=0.6, and we sampled 6 haploid chromosomes per simulation. Simulated sequences contained 45,331 of linked neutral sequence from which we calculated diversity, matching the number of synonymous sites sampled in our empirical analyses on the Y chromosome (see Supporting Information for simulation commands).

>>>>

To parameterize the forward simulations, we estimated the distribution of fitness effects of deleterious mutations (DFE) using our polymorphism data on the X-chromosome with the program DFE-alpha (Keightley and Eyre-Walker ref). This program fits a gamma distribution of selection coefficients to the observed frequency distribution of nonsynonymous and synonymous polymorphism from the population genetic analyses above. We used this estimated gamma distribution in our forward simulations. To examine the expected reduction in diversity, we varied the number of sites under selection, and obtained an approximate likelihood surface for our observed data based on the proportion of simulations that matched the observed estimate of $\pi_{synonymous}$ . To make the simulation output comparable to our data, we initialized the simulations with our empirically estimated autosomal $\theta$, adjusted for the expected neutral reduction in effective population size on the Y chromosome under a sex ratio of Nf/(Nf+Nm)=0.6, and we sampled 6 haploid chromosomes per simulation. Simulated sequences contained 45,331 of linked neutral sequence from which we calculated diversity, matching the number of synonymous sites sampled in our empirical analyses on the Y chromosome (see Supporting Information for simulation commands).
